Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-25 pkg/disttree/inst/draft/rejoinder.Rnw
revision of the two remaining fixmes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2364 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 209e44913af253c0f60e60c82301c4bb03a76f9b

\fixme{This reply needs to be rewritten. It should be listed first
which variables correspond to each other between the models. Then
you can explain that the greater variation in the forest is not
surprising. Finally, it should be pointed out where in the manuscript
this is also discussed.}

Figure 6 shows the variable importance of the distributional forest
for one specific case (similar for other sites and cross-folds) 
using a CRPS based variable importance measure. The subset of 
most important covariates is similar to the set of covariates 
used for the prespecified GAMLSS but not equivalent.
The selection of different variations of the same covariate (cf., Table 2)
is not surprising as the covariates are often highly correlated.
Moreover, in the distributional forest for each node only a randomly
drawn subset of covariates is considered. Hence, if for example the most 
influential covariate is not included in this subset for a specific node 
a similar covariate is very likely to be selected instead.

@@

As you correctly point out, another way to deal with skewness is to
use an extended distributional specification (e.g., Scheuerer and Hamill 2015,
Baran and Nemoda 2016). This increases the complexity of the statistical
models and makes the comparison to publications based on power transformations
more difficult. Therefore, we feel that this exceeds the scope of this
contribution but we do discuss it in Section~4 as being of interest for
future research. 
%\fixme{Include one or two sentences about this as an
%outlook in the discussion of distributional specifications.}

@@

%\fixme{Where should this be pointed out in the manuscript? 
%Z: Both in the introduction when the ``zoo'' of regression techniques
%is introduced -- and again in the discussion (possibly along with
%variable selection?).}

@@

%\fixme{Refer again to the corresponding point in the manuscript.}

@@

\fixme{This also needs to be rewritten (probably best by Reto).
It is a bit frustrating to start the response with comments how instable
all of this is. Instead focus on the insights that are quite
stable across stations.}

Figure 6 is only a visualization of the 10 most important covariates 
of the distributional forest in one particular setting (station Axams, learned 
on 1985--2008). However, this top 10 list is not considered for any specification 
of the boosted GAMLSS for which all available covariates are included. As 
for the distributional forest, we have also calculated variable importance 
based on mean increase of out-of-bag CRPS for the boosted GAMLSS model for 
the exact same setting (station Axams, learned on 1985--2008). The resulting 
top 10 variables are listed in the following barplot.

@@

par(mar = c(4,10,1,2))
barplot(rev(top10_gb), 
        horiz = TRUE, las = 1, axes = FALSE,
        xlab = "Variable importance: mean decrease in CRPS",
        font.axis = 3, #list(family="HersheySerif", face=3),
        # xlim = c(0,1.1),
        xlim = c(0,0.4),
        names.arg = gsub("pow", "", names(rev(top10_gb))))
axis(1, at = seq(0,1.6,0.1), las = 1, mgp=c(0,1,0))
@
\end{center}

Overall it can be stated that the most important covariates of the boosted 
GAMLSS are similar to the ones of the distributional forest even though they
are not exactly the same ones and the influence of \texttt{tp\_max} is clearly
stronger in the boosted GAMLSS. This can be explained by the random selection
of possible split variables in each node of the distributional forest. Thus,
if \texttt{tp\_max} is not available, a similar covariate such as \texttt{tp\_min}
or \texttt{tp\_mean} are very likely to be selected instead while in the boosting
algorithm \texttt{tp\_max} is always a possible choice.

% Out of them, in the exact same setting (Axams, 1985--2008), 
% the boosting algorithm selects 28 covariates 
% for the location parameter, mainly related to precipitation (7) 
% and temperature (11), and 46 covariates for the scale parameter, 
% mainly related to precipitation (10), convective available potential 
% energy (8) and temperature (15).
% mu: 7 tppow, 1 cape, 2 dswrf, 2 msl, 2 pwat, 3 tcolc, 11 temperature
% sigma: 10 tppow, 8 cape, 1 dswrf, 5 msl, 5 pwat, 2 tcolc, 15 temperature

% R> names(coef(gb, parameter = "mu"))
% [1] "bbs(tppow_min)"        "bbs(tppow_max)"        "bbs(tppow_mean1218)"  
% [4] "bbs(tppow_mean1824)"   "bbs(tppow_mean2430)"   "bbs(tppow_sprd0612)"  
% [7] "bbs(tppow_sprd2430)"   "bbs(capepow_sprd0612)" "bbs(dswrf_mean_mean)" 
%[10] "bbs(dswrf_sprd_mean)"  "bbs(msl_sprd_min)"     "bbs(msl_sprd_max)"    
%[13] "bbs(pwat_sprd_min)"    "bbs(pwat_sprd_max)"    "bbs(tcolc_mean_mean)" 
%[16] "bbs(tcolc_mean_max)"   "bbs(tcolc_sprd_mean)"  "bbs(t500_mean_min)"   
%[19] "bbs(t850_mean_min)"    "bbs(t500_sprd_mean)"   "bbs(t500_sprd_max)"   
%[22] "bbs(t700_sprd_mean)"   "bbs(t700_sprd_min)"    "bbs(t700_sprd_max)"   
%[25] "bbs(t850_sprd_min)"    "bbs(t850_sprd_max)"    "bbs(tdiff700850_min)" 
%[28] "bbs(tdiff500700_max)"

% R> names(coef(gb, parameter = "sigma"))
% [1] "bbs(tppow_mean)"       "bbs(tppow_sprd)"       "bbs(tppow_min)"       
% [4] "bbs(tppow_max)"        "bbs(tppow_mean1824)"   "bbs(tppow_mean2430)"  
% [7] "bbs(tppow_sprd0612)"   "bbs(tppow_sprd1218)"   "bbs(tppow_sprd1824)"  
%[10] "bbs(tppow_sprd2430)"   "bbs(capepow_sprd)"     "bbs(capepow_min)"     
%[13] "bbs(capepow_max)"      "bbs(capepow_mean1218)" "bbs(capepow_mean1224)"
%[16] "bbs(capepow_mean1230)" "bbs(capepow_sprd0612)" "bbs(capepow_sprd1218)"
%[19] "bbs(dswrf_sprd_mean)"  "bbs(msl_mean_mean)"    "bbs(msl_mean_max)"    
%[22] "bbs(msl_sprd_mean)"    "bbs(msl_sprd_min)"     "bbs(pwat_mean_mean)"  
%[25] "bbs(pwat_mean_min)"    "bbs(pwat_mean_max)"    "bbs(pwat_sprd_min)"   
%[28] "bbs(pwat_sprd_max)"    "bbs(tmax_mean_mean)"   "bbs(tmax_mean_min)"   
%[31] "bbs(tcolc_mean_min)"   "bbs(tcolc_sprd_max)"   "bbs(t500_mean_mean)"  
%[34] "bbs(t700_mean_mean)"   "bbs(t700_mean_max)"    "bbs(t850_mean_min)"   
%[37] "bbs(t850_mean_max)"    "bbs(t500_sprd_max)"    "bbs(t850_sprd_min)"   
%[40] "bbs(t850_sprd_max)"    "bbs(tdiff700850_min)"  "bbs(tdiff700850_max)" 
%[43] "bbs(tdiff500700_mean)" "bbs(tdiff500700_min)"  "bbs(tdiff500700_max)" 
%[46] "bbs(msl_diff)"

>>>>

The distributional forest selects very similar covariates as included in the
prespecified GAMLSS model. For both models, total precipitation (\texttt{tp})
and total column-integrated condensate (\texttt{tcolc}) are the two most important
covariates. Due to the randomization within the nodes, the distributional forest selects different variations of the same covariate (e.g., \texttt{tp\_max}, \texttt{tp\_mean},
\texttt{tp\_min}; see Figure~6 in the main manuscript and Supplement 2) while
the prespecified GAMLSS mainly only uses one specific variation (\texttt{tp\_max}).
The same is true for variations of \texttt{tcolc\_mean\_*}, \texttt{tcolc\_sprd\_*}
and \texttt{tcolc\_sprd\_*}.

Overall, the covariates selected by the distributional forest do not provide too 
much insights but show that the prespecified GAMLSS model contains an appropriate 
subset of all available covariates.

@@

As you correctly point out, another way to deal with skewness is to
use an extended distributional specification (e.g., Scheuerer and Hamill 2015,
Baran and Nemoda 2016). This increases the complexity of the statistical
models and makes the comparison to publications based on power transformations
more difficult. Therefore, we feel that this exceeds the scope of this
contribution but we do discuss it in Section~4 as being of interest for
future research.

@@

@@

@@

The covariates selected in the distributional forest strongly overlap with the 
ones selected in the boosted GAMLSS. Both methods select variations of the 
forecasted total precipitation (\texttt{tp}) and the total column-integrated 
condensate (\texttt{tcolc}). Due to the randomization in the nodes of the 
trees, different variations of the same covariate (e.g., \texttt{tp\_max}, 
\texttt{tp\_mean}, \texttt{tp\_min}) are selected by the distributional 
forest while the boosted GAMLSS only uses one specific variation (\texttt{tp\_max}). 
The following figure show the CRPS variable importance of the boosted GAMLSS 
model for the very same training and validation period as in Figure~6 in the
manuscript.

@@

par(mar = c(4,10,1,2))
barplot(rev(top10_gb), 
        horiz = TRUE, las = 1, axes = FALSE,
        xlab = "Variable importance: mean increase in CRPS",
        font.axis = 3, #list(family="HersheySerif", face=3),
        # xlim = c(0,1.1),
        xlim = c(0,0.4),
        names.arg = gsub("pow", "", names(rev(top10_gb))))
axis(1, at = seq(0,1.6,0.1), las = 1, mgp=c(0,1,0))
@
\end{center}

Due to graphical reasons, the plots only show the 10 \textit{most important}
covariates based on mean increase in CRPS, however, the models (distributional
forest and boosted GAMLSS) are allowed to use as many covariates as required.
